\cvsection{Working experience}

\begin{cventries}
	\cvexperience
	{2fellows network and design Co., Ltd. (Freelance)}% Workplace
	{Bangkok, Thailand}% Location
	{System Analysts}% Position
	{Dec 2018 - Jan 2019}% Year
	{%
		\begin{cvitem}
			\item {Analyzed the content management system (CMS) and franchise management system.}
			\item {Presented an information of data processes by Data Flow Diagram (DFD).}
			\item {Presented user's interaction with the system by Use case Diagram.}
		\end{cvitem}
	}% Resposibilities
	
	\cvexperience
	{Account Channels (Public) Co., Ltd. (Freelance)}% Workplace
	{Bangkok, Thailand}% Location
	{Web developer (https://e-accountdigital.com/aconline)}% Position
	{Oct 2018 - Jan 2019}% Year
	{%
		\begin{cvitem}
			\item {Analyzed and designed the module of company registration for both front- and back-end website.}
			\item {Developed the web with Bootstrap library, PHP language, and JQuery framework.}
		\end{cvitem}
	}% Resposibilities

	\cvexperience
	{Department of Computer Science, Prince of Songkla University}% Workplace
	{Songkhla, Thailand}% Location
	{12th TOI web developer}% Position
	{Mar 2016 - May 2016}% Year
	{%
		\begin{cvitem}
			\item {Designed the TOI 2016 (Thailand Olympiad in Informatics 2016) website.}
			\item {Developed the website by Python language with JQuery framework.}
			\item {Implemented the web application for both front- and back-end website.} 
		\end{cvitem}
	}% Resposibilities
	
	\cvexperience
	{Department of Information Technology Business, Prince of Songkla University}% Workplace
	{Suratthani, Thailand}% Location
	{Lecturer}% Position
	{May 2013 - Oct 2013}% Year
	{%
		\begin{cvitem}
			\item {Had duty in teaching undergraduate students.}
			\item {Was responsible for teaching in the courses, including the fundamental of computer sciences and computer graphics.} 
		\end{cvitem}
	}% Resposibilities

		\cvexperience
	{Department of Computer Science, Suratthani Rajabhat University}% Workplace
	{Suratthani, Thailand}% Location
	{Lecturer}% Position
	{May 2012 - Apr 2013}% Year
	{%
		\begin{cvitem}
			\item {Had duty in teaching undergraduate students.}
			\item {Was responsible for teaching in the courses, including the fundamental of computer sciences, computer applications, and database systems.}
			\item {Helped run activities and was a part of an academic service to a local school.}
		\end{cvitem}
	}% Resposibilities
\end{cventries}